Who does big team science?

### 2024-11-12 manuscript_definition.Rmd
updating the manuscript analyses, adding two of the outputs and renaming the final output

```{r setup, include = FALSE}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(ggplot2)
library(ggwordcloud)
library(figpatch)
library(RColorBrewer)
library(latex2exp)

@@

# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
              "snip", "ASJC_codes", "snip_all")

var_list_import <- paste0("data/scopus_outputs/", var_list, ".xlsx")

@@

-   Research Question 1: Using current publication values, what should define big team science versus team science? (and change across time)
-   Research Question 2: How has the diversity of those involved in big team science versus team science changed over time?

@@

We used
data from 1970 and forward in the Scopus database, as it is noted online
that this time period includes cited references for calculation of
several of our variables described below. We will analyze our results
based on four subject areas present in the Scopus database: Physical
Sciences, Health Sciences, Social Sciences, and Life Sciences. We
filtered the database to include articles, articles in press, business
articles, conference papers, data papers, preprints, and surveys using
Elsevier's classification system. This project was supported by access
to the Scopus database through the International Center for the Study of
Research.

@@

### RQ1: Publisher Information

We extracted the following information for publication sources: the name
of the publication (source title), subject area (both the large four
subject areas and the smaller four digit all science journal
classification [ASJC] code), and the journal impact using the Source
Normalized Impact per Paper (SNIP).

### RQ2: Publication Information

For each publication of the identified BTS publications, we examined the
full four digit ASJC subject areas codes for each of the larger four
subject areas and the keywords present for these publications.

### RQ3: Author Descriptive Statistics

The author list was extracted from each publication. Next, we used the
author and affiliation arrays to curate a list of all publications and
author information included in BTS papers to calculate the variables
described below.

#### Education

We collected degree information from the author table.
Information on this variable is in the appendix.

#### Types of Publications

We took information from the publication
type variable for each author's publications to present information
about the types of papers BTS authors publish. Information on this
variable is in the appendix.

#### Publication Metrics

For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.

#### Institutions

We report the number of institutions involved in big team science publications.

### RQ4: Author Diversity Statistics

@@

## RQ1: definition shit

>>>>

```{r setup, include = FALSE}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(ggplot2)
library(ggwordcloud)
library(figpatch)
library(RColorBrewer)
library(latex2exp)
library(patchwork)

@@

# things to import
var_list <- c("author_stats", "paper_stats")

var_list_import <- paste0("data/scopus_outputs_2/", var_list, ".xlsx")

@@

-   Research Question 1: Using current publication values, what should define big team science versus team science? 
  - Question 1A: What number of authors and institutional affiliations should designate the differences between team science and big team science?
  - Question 1B: Using the definition from 1A, are there changes in the number of publications over time?

  ### come back to this ###
-   Research Question 2: How has the diversity of those involved in big team science versus team science changed over time?

@@

We used data from 1970 and forward in the Scopus database, as it is noted online
that this time period includes cited references for calculation of
several of our variables described below. We analyzed our results
based on four subject areas present in the Scopus database: Physical
Sciences, Health Sciences, Social Sciences, and Life Sciences. We
filtered the database to include articles, articles in press, business
articles, conference papers, data papers, preprints, and surveys using
Elsevier's classification system. This project was supported by access
to the Scopus database through the International Center for the Study of
Research.

@@

### RQ1: Defining BTS

For each of the publications in Scopus, we calculated the number of distinct authors and institutions. If an author had multiple affiliations, we used the first affiliation listed. Each publication was classified into the four subject areas based on the All Journal Subject Codes present in the database. Publications can be included in multiple subject codes. For example, a medical paper may be listed in both life sciences and health sciences.

### RQ2: Author Diversity Statistics

@@

## RQ1: Defining BTS

```{r total-papers}
total_papers <- 97532104 # the entire database
total_papers_past1970 <- 62966549 # past 1970, in our article types
distinct_authors_past1970 <- 53622443 # all authors

# one row per author per paper with all authors with at least two  
team_author_aff_combo <- 196835398
team_author_aff_papers <- 32454393
team_author_aff_author <- 28353445
team_author_aff_subject_noNA <- 241269297
team_author_aff_papers_noNA <- 32448373
team_author_aff_author_noNA <- 28350468
```

WRITE THE THING --> mention max in the text because too crazy for the graph

```{r stats-authors}
temp_graph <- DF$author_stats %>% 
  filter(SubjectArea != "Multidisciplinary")

auth_plot <- 
  ggplot(temp_graph, aes(x = SubjectArea)) + 
  geom_boxplot(
    aes(
      ymin = Min_Num_Authors,
      lower = lower_IQR,
      middle = Med_Num_Authors,
      upper = upper_IQR,
      ymax = very_high_90
    ),
    stat = "identity"
  ) + 
  theme_bw() + 
  xlab("Subject Area") + 
  ylab("Number of Authors") +
  coord_cartesian(ylim = c(0,12)) + 
  scale_y_continuous(breaks = c(0,2,4,6,8,10,12)) +
  geom_point(aes(x = SubjectArea, y = Average_Num_Authors, 
                 size = SD_Num_Authors)) +
  theme(legend.position = "none")

aff_plot <- 
  ggplot(temp_graph, aes(x = SubjectArea)) + 
  geom_boxplot(
    aes(
      ymin = Min_Num_Aff,
      lower = lower_IQR_Aff,
      middle = Med_Num_Aff,
      upper = upper_IQR_Aff,
      ymax = very_high_90_Aff
    ),
    stat = "identity"
  ) + 
  theme_bw() + 
  xlab("Subject Area") + 
  ylab("Number of First Affiliations") +
  coord_cartesian(ylim = c(0,12)) + 
  scale_y_continuous(breaks = c(0,2,4,6,8,10,12)) +
  geom_point(aes(x = SubjectArea, y = Average_Num_Aff, 
               size = SD_Num_Authors)) +
  theme(legend.position = "none")

auth_plot | aff_plot
```

WRITE THE THING --> make this a table to import

NEED TO RUN ALL TEAMS SUBJECT AREA GRAPH

```{r big-teams, results = 'asis'}
big_teams_papers <- 968765
big_teams_authors <- 4541369

kable(DF$paper_stats %>% 
        arrange(Statistic))
```

##rq1b
